---
title: "Final_Code"
author: "Michael Yan, Kennedy Gachigi, Syamsudin Slamet"
date: "12/2/2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
library(tidyverse)
library(knitr)
```

# CASE I: Bayesian Analysis for Well Specified Model
## Fitting lognormal data with a lognormal model. 
### Simulating, plotting, and estimating the measures. 

```{r CorrectModel}
## defining sample size 
set.seed(53)
n <- c(600, 400, 200)

## Generate data based on different sample sizes
X1 <- rlnorm(n[1], meanlog=1, sdlog=1) 
X2 <- rlnorm(n[2], meanlog=1, sdlog=1)
X3 <- rlnorm(n[3], meanlog=1, sdlog=1)

## Full Bayesian Analysis - True Values for CTE & VaR
True.mu <- exp(1 + 0.50) 
True.VaR <- qlnorm(0.95, meanlog=1, sdlog=1)
d <- function(x){exp(-(log(x)-1)^2/2)/(sqrt(2*pi))}
True.CTE <- (integrate(d, lower=True.VaR, upper=Inf)$value/0.05)

Trues <- cbind(True.mu, True.VaR, True.CTE)
kable(Trues, title="True values")

## Number of iterations and matrices to hold parameter estimates
N <- 10000
keepers1 <- matrix(0, N, 3); keepers2 <- matrix(0, N, 3); keepers3 <- matrix(0, N, 3)

## want to use this to get the meanlog = 1 and sdlog = 1 for est.VaR
## Result on wikipedia 
location <- log(1/sqrt(1+1)); shape <- sqrt(log(1+1))

for (i in 1:N) {
  Y <- rlnorm(n[1], meanlog=1, sdlog=1)
  mu <- mean(Y)
  Z <- rlnorm(n[1], location, shape)
  est.VaR <- qlnorm(0.95, meanlog = mean(Z), sdlog = sqrt(var(Z)))
  est.CTE <- integrate(d, lower=est.VaR, upper=Inf)$value/0.05
  keepers1[i,] <- c(mu,est.VaR,est.CTE)
}

for (j in 1:N) {
  Y2 <- rlnorm(n[2], meanlog=1, sdlog=1)
  mu2 <- mean(Y2)
  Z2 <- rlnorm(n[2], location, shape)
  est.VaR2 <- qlnorm(0.95, meanlog = mean(Z2), sdlog = sqrt(var(Z2)))
  est.CTE2 <- integrate(d, lower=est.VaR2, upper=Inf)$value/0.05
  keepers2[j,] <- c(mu2,est.VaR2,est.CTE2)
}

for (k in 1:N) {
  Y3 <- rlnorm(n[3], meanlog=1, sdlog=1)
  mu3 <- mean(Y3)
  Z3 <- rlnorm(n[3], location, shape)
  est.VaR3 <- qlnorm(0.95, meanlog = mean(Z3), sdlog = sqrt(var(Z3)))
  est.CTE3 <- integrate(d, lower=est.VaR3, upper=Inf)$value/0.05
  keepers3[k,] <- c(mu3,est.VaR3,est.CTE3)
}

par(mfrow=c(1,3))
#Plots of the posterior means
plot(density(keepers1[,1], from = 4, to = 6), main="Mean Estimates", 
     xlab = "Mu", ylim = c(0, 2), lwd = 5, col = "Green")
par(new=T)
plot(density(keepers2[,1], from = 4, to = 6), main = "", 
     xlab = "", ylim = c(0,2), lty = 3, lwd = 5, col = "Red")
par(new=T)
plot(density(keepers3[,1], from = 4, to = 6), main = "", 
     xlab = "", ylim = c(0,2), lty = 2, lwd = 5, col = "Brown")
par(new=T)
points(True.mu, 0, pch = "X")
legend("topright", title = "Sample Sizes", legend =c("n=600", "n=400", "n=200"), 
       col = c("Green", "Red", "Brown"), bg="lightblue", lwd=5, lty=1:3)

#Plots of the VaR for different sample sizes
plot(density(keepers1[,2], from = 0, to = 100), main="Var Estimates", 
     xlab = "VaR", ylim = c(0,0.2), lwd = 5, col = "Green")
par(new=T)
plot(density(keepers2[,2], from = 0, to = 100), main = "", 
     xlab = "", ylim = c(0,0.2), lty = 3, lwd = 5, col = "Red")
par(new=T)
plot(density(keepers3[,2], from = 0, to = 100), main = "", 
     xlab = "", ylim = c(0,0.2), lty = 2, lwd = 5, col = "Brown")
par(new=T)
points(True.VaR, 0, pch = "X")
legend("topright", title = "Sample Sizes", legend =c("n=600", "n=400", "n=200"), 
       col = c("Green", "Red", "Brown"), bg="lightblue", lwd=5, lty=1:3)

#Plots of the CTE for different sample sizes. 
plot(density(keepers1[,3], from = 0, to = 100), main="CTE Estimates", 
     xlab = "CTE", ylim = c(0, 0.10), lwd = 5, col = "Green")
par(new=T)
plot(density(keepers2[,3], from = 0, to = 100), main = "", 
     xlab = "", ylim = c(0,0.1), lty = 3, lwd = 5, col = "Red")
par(new=T)
plot(density(keepers3[,3], from = 0, to = 100), main = "", 
     xlab = "", ylim = c(0,0.1), lty = 2, lwd = 5, col = "Brown")
par(new=T)
points(True.CTE, 0, pch = "X")
legend("topright", title = "Sample Sizes", legend =c("n=600", "n=400", "n=200"), 
       col = c("Green", "Red", "Brown"), bg="lightblue", lwd=5, lty=1:3)
```

# CASE II: Bayesian Analysis for Misspecified Model
## Fitting lognormal data with a gamma model. 
### Simulating, plotting, and estimating the measures. 
```{r IncorrectModel}
set.seed(53) 
alpha <- 3; lambda <- 0.2 
n <- c(600, 400, 200); N <- 500; h <- 0.2 
X <- rlnorm(n[1], meanlog=1, sdlog=1) 

shape <- n*alpha+1 
rate1 <- lambda+sum(X) 
rate2 <- lambda+sum(X[1:400])
rate3 <- lambda+sum(X[1:200])

## Estimating the mean for the posterior 

Y1 <- rgamma(N, shape=shape[1], rate=rate1)
Y2 <- rgamma(N, shape=shape[2], rate=rate2)
Y3 <- rgamma(N, shape=shape[3], rate=rate3)

mu1 <- alpha/Y1; mu2 <- alpha/Y2; mu3 <- alpha/Y3

f1.hat <- function(x){
  y <- mean(dnorm((x-mu1)/h))/h
  return(y)
}

f2.hat <- function(x){
  y <- mean(dnorm((x-mu2)/h))/h
  return(y)
}

f3.hat <- function(x){
  y <- mean(dnorm((x-mu3)/h))/h
  return(y)
}

x <- seq(3.5, 5.5, 0.01)
y1 <- sapply(x, f1.hat)
y2 <- sapply(x, f2.hat)
y3 <- sapply(x, f3.hat)

plot(x, y1, type="l", xlim=c(3.5, 5.5), ylim=c(0, 2), lty=1, xlab="mean", 
     ylab="posterior density", main = "Plot of the posterior mean", 
     col = "Green", lwd = 5)
par(new=T)
plot(x, y2, type="l", xlim=c(3.5, 5.5), ylim=c(0, 2), lty=2, xlab="", ylab="", 
     col = "Red", lwd = 5)
par(new=T)
plot(x, y3, type="l", xlim=c(3.5, 5.5), ylim=c(0, 2), lty=3, xlab="", ylab="", 
     col = "Brown", lwd = 5)
par(new=T)
points(4.482 , 0, pch = "X")
legend("topleft", title = "Sample Sizes", legend =c("n=600", "n=400", "n=200"), 
       col = c("Green", "Red", "Brown"), bg="lightblue", lwd=5, lty=1:3)

# Estimating VaR of the posterior 

VaR.star <- qlnorm(0.95, meanlog=1, sdlog=1)
d <- function(x){exp(-(log(x)-1)^2/2)/(sqrt(2*pi))}
CTE.star <- integrate(d, lower=VaR.star, upper=Inf)$value/0.05

g <- function(x){
  y <- qgamma(0.95, shape=3, rate=x)
  return(y)
}
VaR1 <- sapply(Y1, g)
VaR2 <- sapply(Y2, g)
VaR3 <- sapply(Y3, g)

g1.hat <- function(x){ 
  y <- mean(dnorm((x-VaR1)/h))/h
  return(y)
}

g2.hat <- function(x){ 
  y <- mean(dnorm((x-VaR2)/h))/h
  return(y)
}

g3.hat <- function(x){ 
  y <- mean(dnorm((x-VaR3)/h))/h
  return(y)
}

x <- seq(7, 12, 0.01)
y1 <- sapply(x, g1.hat)
y2 <- sapply(x, g2.hat)
y3 <- sapply(x, g3.hat)

plot(x, y1, type="l", xlim=c(7, 12), ylim=c(0, 1.5), xlab="VaR", 
     ylab="posterior density", main = "Plot of the VaR estimate", 
     col = "Green", lwd = 5, lty=1)
par(new=T)
plot(x, y2, type="l", xlim=c(7, 12), ylim=c(0, 1.5), xlab="", ylab="", 
     col = "Red", lwd = 5, lty=2)
par(new=T)
plot(x, y3, type="l", xlim=c(7, 12), ylim=c(0, 1.5), xlab="", ylab="", 
     col = "Brown", lwd = 5, lty=3)
par(new=T)
points(9.411, 0, pch = "X")
legend("topleft", title = "Sample Sizes", legend =c("n=600", "n=400", "n=200"), 
       col = c("Green", "Red", "Brown"), bg="lightblue", lwd=5, lty=1:3)

##

# Estimating CTE of the posterior 

b <- function(theta){
  integrand<-function(x){x*dgamma(x, shape=3, rate=theta)}
  y<-integrate(integrand, lower=qgamma(0.95, 3, theta), upper=Inf)$value/0.05  
  return(y)
}

CTE1 <- sapply(Y1, b)
CTE2 <- sapply(Y2, b)
CTE3 <- sapply(Y3, b)

h1.hat<-function(x){
  y<-mean(dnorm((x-CTE1)/h))/h
  return(y)
}

h2.hat<-function(x){
  y<-mean(dnorm((x-CTE2)/h))/h
  return(y)
}

h3.hat<-function(x){
  y<-mean(dnorm((x-CTE3)/h))/h
  return(y)
}

x <- seq(9, 15, 0.01)
y1 <- sapply(x, h1.hat)
y2 <- sapply(x, h2.hat)
y3 <- sapply(x, h3.hat)

##Plot is on beginning of next page 
plot(x, y1, type="l", xlim=c(9, 15),  ylim=c(0, 1.5), 
     xlab="CTE", ylab="posterior density", 
     main = "Plot of the CTE estimate", 
     col = "Green", lwd = 5, lty=1)
par(new=T)
plot(x, y2, type="l", xlim=c(9, 15), ylim=c(0, 1.5), 
     lty=2, xlab="", ylab="", col = "Red", lwd = 5)
par(new=T)
plot(x, y3, type="l", xlim=c(9, 15), ylim=c(0, 1.5), lty=3, xlab="", ylab="", 
     col = "Brown", lwd = 5)
par(new=T)
points(11.363, 0, pch = "X")
legend("topleft", title = "Sample Sizes", legend =c("n=600", "n=400", "n=200"), 
       col = c("Green", "Red", "Brown"), bg="lightblue", lwd=5, lty=1:3)
```

# CASE III: Gibbs Posterior and Credibility Estimation
## Fitting a normal model on lognormal data. 
### Simulating, plotting, and estimating the measures.

```{r Gibbs}
## defining our sample size
set.seed(100)
n <- c(600, 400, 200)

#generate random number log normal distribution, for different n. 
G1 <- rlnorm(n[1], meanlog=1, sdlog=1) 
G2 <- rlnorm(n[2], meanlog=1, sdlog=1)
G3 <- rlnorm(n[3], meanlog=1, sdlog=1)

#Define true parameter values
True.Mu <- exp(1 + 0.50)
VaR.True <- qlnorm(0.95, meanlog=1, sdlog=1)
d <- function(x){exp(-(log(x)-1)^2/2)/sqrt(2*pi)}
CTE.True <- integrate(d, lower=VaR.True, upper=Inf)$value/0.05

## Number of iterations
N = 10000

## Matrices to hold our measure values
keepersA <- matrix(0, N, 3); keepersB <- matrix(0, N, 3); keepersC <- matrix(0, N, 3)

## variances of the gibbs posterior. 
sigma2.n1 <- n[1]/((n[1]/(var(G1)) + 1))
sigma2.n2 <- n[2]/((n[2]/(var(G2)) + 1))
sigma2.n3 <- n[3]/((n[3]/(var(G3)) + 1))

## Generating measure values for n = 600. 
for (m in 1:N) {
  R1 <- rnorm(n[1], mean=mean(G1), sd=sqrt(sigma2.n1))
  mu1 <- mean(R1)
  VaR.est1 <- qnorm(0.95, mean = mean(R1), sd = sqrt(var(R1)))
  CTE.est1 <- integrate(d, lower=VaR.est1, upper=Inf)$value/0.05
  keepersA[m,] <- c(mu1,VaR.est1,CTE.est1)
}

## Generating measure values for n = 400. 
for (q in 1:N) {
  R2 <- rnorm(n[2], mean=mean(G2), sd=sqrt(sigma2.n2))
  mu2 <- mean(R2)
  VaR.est2 <- qnorm(0.95, mean = mean(R2), sd = sqrt(var(R2)))
  CTE.est2 <- integrate(d, lower=VaR.est2, upper=Inf)$value/0.05
  keepersB[q,] <- c(mu2,VaR.est2,CTE.est2)
}

## Generating measure values for n = 200. 
for (t in 1:N) {
  R3 <- rnorm(n[3], mean=mean(G3), sd=sqrt(sigma2.n3))
  mu3 <- mean(R3)
  VaR.est3 <- qnorm(0.95, mean = mean(R3), sd = sqrt(var(R3)))
  CTE.est3 <- integrate(d, lower=VaR.est3, upper=Inf)$value/0.05
  keepersC[t,] <- c(mu3,VaR.est3,CTE.est3)
}

par(mfrow=c(1,3))
#Plot densities of the posterior means for different sample size
plot(density(keepersA[,1], from = 4, to = 6), main="Mean Estimates", xlab = "Mu", 
     ylim = c(0, 2), lwd = 5, col = "Green")
par(new=T)
plot(density(keepersB[,1], from = 4, to = 6), main = "", xlab = "", 
     ylim = c(0,2), lty = 3, lwd = 5, col = "Red")
par(new=T)
plot(density(keepersC[,1], from = 4, to = 6), main = "", xlab = "", 
     ylim = c(0,2), lty = 2, lwd = 5, col = "Brown")
par(new=T)
points(True.Mu, 0, pch = "X")
legend("topright", title = "Sample Sizes", legend =c("n=600", "n=400", "n=200"), 
       col = c("Green", "Red", "Brown"), bg="lightblue", lwd=5, lty=1:3)

#Plot densities of the VaR for different sample sizes
plot(density(keepersA[,2], from = 10, to = 20), main="Var Estimates", xlab = "VaR", 
     ylim = c(0,2.0), lwd = 5, col = "Green")
par(new=T)
plot(density(keepersB[,2], from = 10, to = 20), main = "", xlab = "", 
     ylim = c(0,2.0), lty = 3, lwd = 5, col = "Red")
par(new=T)
plot(density(keepersC[,2], from = 10, to = 20), main = "", xlab = "", 
     ylim = c(0,2.0), lty = 2, lwd = 5, col = "Brown")
par(new=T)
points(VaR.True, 0, pch = "X")
legend("topright", title = "Sample Sizes", legend =c("n=600", "n=400", "n=200"), 
       col = c("Green", "Red", "Brown"), bg="lightblue", lwd=5, lty=1:3)

#Plot densities of the CTE for different sample sizes. 
plot(density(keepersA[,3], from = 18, to = 28), main="CTE Estimates", xlab = "CTE", 
     ylim = c(0, 1.0), lwd = 5, col = "Green")
par(new=T)
plot(density(keepersB[,3], from = 18, to = 28), main = "", xlab = "", 
     ylim = c(0,1.0), lty = 3, lwd = 5, col = "Red")
par(new=T)
plot(density(keepersC[,3], from = 18, to = 28), main = "", xlab = "", 
     ylim = c(0,1.0), lty = 2, lwd = 5, col = "Brown")
par(new=T)
points(CTE.True, 0, pch = "X")
legend("topright", title = "Sample Sizes", legend =c("n=600", "n=400", "n=200"), 
       col = c("Green", "Red", "Brown"), bg="lightblue", lwd=5, lty=1:3)
```